Figures

### 2019-05-22 figures/08_exploratory_dotplot.Rmd
remake dotplot with dt_scaled

dt       <- readRDS("../data/dt_scaled.rds")
dt_sub   <- dt %>% 
  dplyr::select(tp, tn, lake_area_ha:wheat, 
                matches("cultivated_crops")) %>%
  dplyr::select(-row_crop_pct, -ag_pct, -pasture_pct) %>% # rm nlcd
  dplyr::select(-mixed.crop, -matches("other"), -forage, 
                -hu12_ppt_std, -water, -developed, -forest) %>% # rm junk
  dplyr::filter(complete.cases(.)) %>%
  mutate_all(as.numeric) %>%
  data.frame(stringsAsFactors = FALSE)

@@

prep_dotplot <- function(x, col_name){
  pred_key <- read.csv("../data/predictor_key.csv", stringsAsFactors = FALSE)
  res      <- 
    dplyr::select(x, UQ(rlang::sym(col_name))) %>%
    dplyr::mutate(var = row.names(x)) %>%
    dplyr::left_join(pred_key, by = "var") %>%
    dplyr::mutate(var = factor(row.names(x), 
                            levels = rev(row.names(x))), 
                  pretty = factor(pretty, levels = rev(pretty)),
                  category = factor(category, 
                                    levels = c("Lake", "Nutrient sources",
                                               "Nutrient proxies",
                                               "Transport capacity"))) %>%
    dplyr::filter(!(var %in% c("tp", "tn")))
  res
}

@@

# head(prep_dotplot(dt_tp, "tp"))
# show_col(brewer_pal("div", "Set1")(4))                   
gg_tp <-  ggplot(data = prep_dotplot(dt_tp, "tp")) + 
    geom_point(aes(x = tp, y = pretty, color = category)) + 
    scale_color_brewer(palette = "Set1") +
    xlim(0, 0.5) +
    plot_opts
gg_tn <- ggplot(data = prep_dotplot(dt_tn, "tn")) + 
    geom_point(aes(x = tn, y = pretty, color = category)) +
    scale_color_brewer(palette = "Set1") +
    xlim(0, 0.5) +
    plot_opts
legend_b <- get_legend(gg_tp + 
                         theme(legend.position="bottom", 
                               legend.justification = "center", 
                               legend.text = element_text(size = 10), 
                               legend.title = element_blank()))
plot_grid(
  plot_grid(gg_tp, gg_tn), 
  legend_b, ncol = 1, rel_heights = c(1, 0.1))

@@

ggplot(data = tidyr::gather(dt_sub)) + 
  geom_density(aes(value)) +
  facet_wrap_paginate(~key, scales = "free", ncol = 2, nrow = 4, page = 1)
ggplot(data = tidyr::gather(dt_sub)) + 
  geom_density(aes(value)) +
  facet_wrap_paginate(~key, scales = "free", ncol = 2, nrow = 4, page = 2)
ggplot(data = tidyr::gather(dt_sub)) + 
  geom_density(aes(value)) +
  facet_wrap_paginate(~key, scales = "free", ncol = 2, nrow = 4, page = 3)
ggplot(data = tidyr::gather(dt_sub)) + 
  geom_density(aes(value)) +
  facet_wrap_paginate(~key, scales = "free", ncol = 2, nrow = 4, page = 4)

>>>>

dt       <- readRDS("../data/dt_scaled.rds")
dt_sub   <-  dt %>% 
  dplyr::select(-lagoslakeid) %>%
  # dplyr::select(tp, tn, lake_area_ha:wheat, 
  #               matches("cultivated_crops")) %>%
  # dplyr::select(-row_crop_pct, -ag_pct, -pasture_pct) %>% # rm nlcd
  # dplyr::select(-mixed.crop, -matches("other"), -forage, 
  #               -hu12_ppt_std, -water, -developed, -forest) %>% # rm junk
  # dplyr::filter(complete.cases(.)) %>%
  mutate_all(as.numeric) %>%
  janitor::remove_empty("cols") %>%
  data.frame(stringsAsFactors = FALSE)

# cor.test(dt_sub$nitrogen_atmospheric_deposition, dt_sub$tp)

@@

prep_dotplot <- function(x, col_name){
  # x <- dt_tp
  # col_name <- "tp"
  pred_key <- read.csv("../data/predictor_key.csv", stringsAsFactors = FALSE)
  res      <- x %>%
    dplyr::select(UQ(rlang::sym(col_name))) %>%
    # dplyr::filter(!is.na(UQ(rlang::sym(col_name)))) %>%
    dplyr::mutate(var = row.names(x)) %>%
    dplyr::left_join(pred_key, by = "var") %>%
    dplyr::mutate(var = factor(row.names(x), 
                            levels = rev(row.names(x))), 
                  pretty = factor(pretty, levels = rev(pretty)),
                  category = factor(category, 
                                    levels = c("Lake", "Nutrient sources",
                                               "Nutrient proxies",
                                               "Transport capacity"))) %>%
    dplyr::filter(!(var %in% c("tp", "tn")))
  res
}

@@

# head(prep_dotplot(dt_tp, "tp"))
# show_col(brewer_pal("div", "Set1")(4))                   
gg_tp <-  ggplot(data = prep_dotplot(dt_tp, "tp")) + 
    geom_point(aes(x = tp, y = pretty, color = category)) + 
    scale_color_brewer(palette = "Set1") +
    xlim(0, 0.6) +
    plot_opts
gg_tn <- ggplot(data = prep_dotplot(dt_tn, "tn")) + 
    geom_point(aes(x = tn, y = pretty, color = category)) +
    scale_color_brewer(palette = "Set1") +
    xlim(0, 0.6) +
    plot_opts
legend_b <- get_legend(gg_tp + 
                         theme(legend.position="bottom", 
                               legend.justification = "center", 
                               legend.text = element_text(size = 10), 
                               legend.title = element_blank()))
plot_grid(
  plot_grid(gg_tp, gg_tn), 
  legend_b, ncol = 1, rel_heights = c(1, 0.1))

@@

ggplot(data = tidyr::gather(dt_sub)) +
  geom_density(aes(value)) +
  facet_wrap_paginate(~key, scales = "free", ncol = 2, nrow = 4, page = 1)
ggplot(data = tidyr::gather(dt_sub)) +
  geom_density(aes(value)) +
  facet_wrap_paginate(~key, scales = "free", ncol = 2, nrow = 4, page = 2)
ggplot(data = tidyr::gather(dt_sub)) +
  geom_density(aes(value)) +
  facet_wrap_paginate(~key, scales = "free", ncol = 2, nrow = 4, page = 3)
